% ==================== REFERENCES ====================
\begin{thebibliography}{99}

\item[] \textbf{\large Books}

\bibitem{aggarwal2016}
Aggarwal, C. C. (2016). \textit{Recommender Systems: The Textbook}. Springer.

\bibitem{falk2019}
Falk, K. (2019). \textit{Practical Recommender Systems}. Manning Publications.

\bibitem{ricci2022}
Ricci, F., Rokach, L., \& Shapira, B. (2022). \textit{Recommender Systems Handbook} (3rd ed.). Springer.

\bibitem{aliev2026}
Aliev, R. (2026). \textit{Recommender Algorithms: A Practitioner's Guide}.

\item[] \textbf{\large Academic Papers \& Journals}

\bibitem{covington2016}
Covington, P., Adams, J., \& Sargin, E. (2016). Deep Neural Networks for YouTube Recommendations. \textit{Proceedings of the 10th ACM Conference on Recommender Systems}, 191--198.

\bibitem{portugal2015}
Portugal, I., Alencar, P., \& Cowan, D. (2015). The Use of Machine Learning Algorithms in Recommender Systems: A Systematic Review. \textit{arXiv preprint arXiv:1511.05263}.

\bibitem{zhang-rspapers}
Zhang, H. (n.d.). \textit{RSTutorials: A Curated List of Must-read Papers on Recommender System}. GitHub Repository. Retrieved from \url{https://github.com/hongleizhang/RSPapers}

\item[] \textbf{\large Datasets}

\bibitem{sentiment140}
Bollen, J., Mao, H., \& Zeng, X. (2009). \textit{Sentiment140 Dataset}.

\bibitem{snap2014}
Leskovec, J., \& Krevl, A. (2014). \textit{Stanford Network Analysis Project (SNAP) Twitter Network Dataset}. Stanford University.

\bibitem{recsys2020}
Twitter Inc.\ \& ACM RecSys. (2020). \textit{RecSys Challenge 2020: Twitter Public Engagements Dataset}. Academic Torrents.

\bibitem{kaggle-twitter}
Various Contributors. (n.d.). \textit{Twitter Friends Dataset}. Kaggle.

\item[] \textbf{\large Documentation \& Source Code}

\bibitem{gorse-docs}
Gorse Open-Source AutoML Recommender Engine. (2026). \textit{Official Documentation}. Retrieved from \url{https://gorse.io}

\bibitem{typesense-docs}
Typesense. (2026). \textit{Typesense Vector Search Documentation (HNSW Algorithms)}. Retrieved from \url{https://typesense.org}

\bibitem{x-algorithm}
X Corp (formerly Twitter). (2023). \textit{X (Twitter) Recommendation Algorithm Source Code}. GitHub. Retrieved from \url{https://github.com/xai-org/x-algorithm}

\end{thebibliography}
